### 2016-09-22 R/ITHIM.Rmd
Fixed bug in ITHIM.default update

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = FALSE, warning = FALSE}
upper <- 20
length <- 100

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")
ITHIM.default <- updateITHIM(ITHIMList[[HHS]], "cvNonTravel", 3)
ITHIM.default <- updateITHIM(ITHIMList[[HHS]], "cv", 3.0288)
ITHIM.default <- updateITHIM(ITHIMList[[HHS]], "pWalk", 0.85)

>>>>

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = FALSE, warning = FALSE}
upper <- 50
length <- 500

DALYsTotal <- data.frame()
ITHIMList <- list()
ITHIM.default <- createITHIM(vision = "baseline", region = "national")
ITHIM.default <- updateITHIM(ITHIM.default, "cvNonTravel", 3)
ITHIM.default <- updateITHIM(ITHIM.default, "cv", 3.0288)
ITHIM.default <- updateITHIM(ITHIM.default, "pWalk", 0.85)
ITHIM.default <- updateITHIM(ITHIM.default, "quantiles", (1:99)/100)
